Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-30 qpip0.tex
Smooth out discussions of Mahadev's PiMeasure

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
Intuitively, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover. The prover commits to a state $\rho$ of its choice using $pk$ and replies with its commitment. The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply. \cite{FOCS:Mahadev18a} shows a ``binding" property of $\PiMeasure$: if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ the verifier has picked at the beginning.

>>>>

In her groundbreaking work, Mahadev gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
Specifically, the verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$, before sending $pk$ to the prover. The prover commits to a state $\rho$ of its choice using $pk$ and replies with its commitment. The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply. \cite{FOCS:Mahadev18a} shows a ``binding" property of $\PiMeasure$: if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ the verifier has picked at the beginning.
